Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-05-31 analysis/paper/paper.qmd
Figure 1

  fig-path: "../figures/"

@@

@@

@@

```{r}
#| label: fig-top6map

plot(1, 1)

>>>>

@@

knitr:
  opts_chunk: 
    dev: # Output figures as .png and .eps 
      - png
      - postscript 
    fig.path: "../figures/"

@@

```{r}
#| label: load
#| echo: false

# Load this analysis as a package
devtools::load_all()

@@

```{r}
#| label: fig-top6map
#| fig-cap: "Geographic distributions of the 6 most abundant species observed during the surveys, averaged across survey years: (A) Adélie penguin, (B) Antarctic fur seal, (C) Antarctic petrel, (D) crabeater seal, (E) snow petrel, (F) southern fulmar. Unlike the cluster analysis, these maps aggregate sightings from all visual surveys within the study area. The sightings associated with sites are a subset of these (i.e. sightings more than 15 km or 3 d from a sampling station are included here)."
#| out-width: 169mm
#| out-height: 121mm

make_fig_top6map(read_obj("topsix_clim_class", rast = TRUE))
